Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/intro.tex
Fixed some wrapping issues

Wearable devices offer many compelling opportunities for benefiting users.  For instance, they could enable a more natural, human-centered interface experience and a healthier, fitness-data inspired lifestyle. There will likely be many more applications in the future which take advantage of data captured by wearable devices.

However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent. Even though wearable technology is currently in early stages, we have already seen instances of these risks. For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information. Public discomfort toward facial recognition caused Google to prohibit Google Glass apps from using facial recognition~\cite{GlassDetection}, and public concerns about privacy may have partly contributed to Google's discontinuation of Glass~\cite{14_dvorak_2014,1_russell_2014, 15_mashable_2014, 16_gross_2014}.

We have seen similar privacy \cite{kelley2013privacy, sadeh2009understanding, shklovski2014leakiness} and security issues \cite{enck2011study, felt2011survey} related to data capture on smartphones. Mobile platforms have tried to address the risks by communicating data capture to users as the data is captured. However, many users are habituated to these notifications, because they see them all the time, often for things that they do not care about \cite{felt2012android}. Once habituated to seemingly benign privacy and security warnings, users tend to ignore more sensitive warnings that are similarly designed~\cite{Egelman08}.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item We compare users' perceptions of a range of privacy and security risks of wearables. We found that user concern is driven more by the type of data being captured than the recipient of the data.
\item Our results shed light into how users feel about various data recipients. We observed that users make less distinction between sharing data with friends, co-workers, and the general public, compared to sharing with an application's servers.
\item We analyze users' self-reported top concerns regarding wearable devices. The results give an sense of what broad concerns users have, which can be used to guide future research in unexplored use cases. 
\item We examine how serious users perceive the risks of wearables to be, compared to risks associated with more familiar technologies. Most of our participants saw wearables' new capabilities as benign, though we suspect that this could be due to a lack of exposure to these newer technologies.
\end{itemize}

>>>>

Wearable devices offer many compelling opportunities for benefiting users.  For instance, they could enable more natural, human-centered interface experiences and healthier, fitness-data inspired lifestyles. There will likely be many more applications in the future that take advantage of data captured by wearable devices. However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent. Even though wearable technology is currently in early stages, we have already seen manifestations of these risks. For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information. Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, and public concerns about privacy may have partly contributed to Google's discontinuation of Glass~\cite{14_dvorak_2014,1_russell_2014, 15_mashable_2014, 16_gross_2014}.

Similar privacy~\cite{kelley2013privacy, sadeh2009understanding, shklovski2014leakiness} and security issues~\cite{enck2011study, felt2011survey} pervade smartphones. Mobile platforms have tried to address the risks by communicating data capture to users. However, many users are habituated to these notifications, because they see them frequently, often for things that they do not care about~\cite{felt2012android}. Once habituated to seemingly benign privacy and security warnings, users tend to ignore more sensitive warnings that are similarly designed~\cite{Egelman08}.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item We compare users' perceptions of a range of privacy and security risks of wearables. We found that user concern is driven more by the type of data being captured than the recipient of the data.
\item We shed light on how users feel about various data recipients. We observed that users make less distinction between sharing data with friends, co-workers, and the general public, compared to sharing with an application's servers (the latter is viewed as less concerning).
\item We analyze users' self-reported top concerns regarding wearable devices. The results give a sense of what broad concerns users have, which can be used to guide future research on unexplored use cases. 
\item We examine how serious users perceive the risks of wearables to be, compared to risks associated with more familiar technologies. Most of our participants saw wearables' new capabilities as benign, though we suspect that this could be due to a lack of exposure to these newer technologies.
\end{itemize}
